---
title: "**Panel Data and DID**"
institute: "**Business school,Nanjing University**"
author: "Jing Bu"
date: "12/27/2018"
header-includes:
    \usepackage{ctex}
    \usepackage{color}
    \usepackage{amsmath}
#output: 
#  beamer_presentation:
documentclass: ctexart
output:
  rticles::ctex:
     fig_caption: yes
     number_sections: yes
     toc: yes
classoption: "hyperref,"
#    colortheme: dolphin
#    fonttheme: professionalfonts
#    latex_engine: xelatex
#    theme: CambridgeUS
#    toc: false
#    incremental: false
---

# Panel Data

- Panel data (also known as longitudinal or cross-sectional time-series data) is a dataset in which the behavior of entities are observed across time.
These entities could be states, companies, individuals, countries, etc.

## Exploring panel data

```{r echo=TRUE,warning=FALSE}
library("foreign")
Panel <-read.dta("/Users/admin/Desktop/teaching assiatant/Econometrics/teaching assistant slides/R/traffic.dta")
#install.packages("car")
library("car")
scatterplot(fatal~year|state,data=Panel)
```

```{r echo=TRUE,warning=FALSE}
library("foreign")
library("car")
Panel1 <-read.dta("http://dss.princeton.edu/training/Panel101.dta")
scatterplot(y~year|country, data=Panel1)
```

## Fixed Effects Model

```{r echo=TRUE,warning=FALSE}
#install.packages("gplots")
library("gplots")
plotmeans(fatal ~ state, main="Heterogeineity across countries", data=Panel)
```

```{r echo=TRUE,warning=FALSE}
library("gplots")
plotmeans(fatal ~ year, main="Heterogeineity across years", data=Panel)
```

### OLS

```{r echo=TRUE,warning=FALSE}
ols<-lm(fatal ~ beertax+spircons+unrate+perinck, data=Panel)
summary(ols)
```

- Regular OLS regression does not consider heterogeneity across groups or time

### Least squares dummy variable model

```{r echo=TRUE,warning=FALSE}
fixed.dum <-lm(fatal ~ beertax+spircons+unrate+perinck+factor(state), data=Panel)
summary(fixed.dum)
```

### Fixed effects: n entity-specific intercepts (using plm)

```{r echo=TRUE,warning=FALSE}
#install.packages("plm")
library("plm")
fixed <-plm(fatal ~ beertax+spircons+unrate+perinck, data=Panel, index=c("state", "year"), model="within")
summary(fixed)
```

### Test£ºfixed or ols?

```{r echo=TRUE,warning=FALSE}
pFtest(fixed, ols)
```

# Difference in differences

```{r echo=TRUE,warning=FALSE}
library("foreign")
mydata <-read.dta("/Users/admin/Desktop/teaching assiatant/Econometrics/teaching assistant slides/R/cardkrueger1994.dta")
```

- Create an interaction between time and treated. We will call this interaction *did*.

- $did=t:treated$

```{r echo=TRUE}
didreg <- lm(fte ~ treated + t + t:treated, data = mydata)
summary(didreg)
```

- The coefficient for *did* is the differences-in-differences estimator.The effect is significant at 10% with the treatment having a positive effect.


