---
title: "**Regression-discontinuity designs**"
institute: "**Business school,Nanjing University**"
author: "Jing Bu"
date: "12/13/2018"
header-includes:
    \usepackage{ctex}
    \usepackage{color}
    \usepackage{amsmath}
#output: 
#  beamer_presentation:
documentclass: ctexart
output:
  rticles::ctex:
     fig_caption: yes
     number_sections: yes
     toc: yes
classoption: "hyperref,"
#    colortheme: dolphin
#    fonttheme: professionalfonts
#    latex_engine: xelatex
#    theme: CambridgeUS
#    toc: false
#    incremental: false
---

# Preparation

## Import Data
```{r echo=TRUE}
#install.packages("foreign")
library("foreign")
votex<-read.dta("/Users/admin/Desktop/teaching assiatant/Econometrics/teaching assistant slides/R/votex.dta")
```

## Data
```{r echo=TRUE}
str(votex)
```

## Load rddtools package
```{r echo=TRUE,warning=FALSE}
#install.packages("devtools")
#devtools::install_github("bquast/rddtools")
library("rddtools")
```

## Set outcome, forcing and cutoff variable
```{r echo=TRUE,warning=FALSE}
votex_rdd <- rdd_data(x=d, y=lne,cutpoint=0, data=votex)
```

## Summary and Plot
```{r echo=TRUE,warning=FALSE}
summary(votex_rdd)
plot(votex_rdd,nbins=50)
```

# Estimate RDD

## Parametric estimation 

```{r echo=TRUE,warning=FALSE}
library("rddtools")
reg_para<-rdd_reg_lm(votex_rdd,slope="separate",order = 1)
print(reg_para)
plot(reg_para,ylim=c(21,21.5))
```

## Nonparametric estimation

```{r echo=TRUE,warning=FALSE}
reg_np <- rdd_reg_np(rdd_object=votex_rdd, slope = "separate")
print(reg_np)
plot(reg_np,ylim=c(21,21.5))
```

- **Reference**
- Guido Imbens & Karthik Kalyanaraman,2012,**"Optimal Bandwidth Choice for the Regression Discontinuity Estimator"**, *Review of Economic Studies*,Vol.79(3),933-959

## Covariates
```{r echo=TRUE,warning=FALSE}
votex_rdd_cov <- rdd_data(x=d, y=lne,cutpoint=0, data=votex,covar=c(votex$i,votex$votpop,votex$black))
summary(votex_rdd_cov)
```

```{r echo=TRUE,warning=FALSE}
library("rddtools")
reg_para_cov<- rdd_reg_lm(rdd_object=votex_rdd_cov,slope="separate",covariates=c(votex$i,votex$votpop,votex$black))
print(reg_para_cov)
plot(reg_para_cov,ylim=c(21,21.5))
```

```{r echo=TRUE,warning=FALSE}
reg_np_cov <- rdd_reg_np(rdd_object=votex_rdd_cov, slope = "separate",covariates=c(votex$i,votex$votpop,votex$black))
print(reg_np_cov)
plot(reg_np_cov,ylim=c(21,21.5))
```

# Regression sensitivity analysis

```{r echo=TRUE,warning=FALSE}
plotSensi(reg_np,0,1,level = 0.95, output = c("data", "ggplot"), plot = TRUE)
```

# Placebo Tests
```{r echo=TRUE}
plotPlacebo(reg_para, device = "ggplot",level = 0.95)
```

```{r echo=TRUE}
plotPlacebo(reg_np, device = "ggplot",level = 0.95)
```

# Design sensitivity analysis
```{r echo=TRUE}
dens_test(reg_para)
```

- **Reference**
- Justin McCrary,2008,**"Manipulation of the running variable in the regression discontinuity design:A density test"**,*Journal of Econometrics*, Vol.142(2) ,698-714

